### 2020-03-14 paper/sections/design.tex
change the figure format
improve consistency

A brief framework of AdaCompress is shown in Figure \ref{fig: framework}. Briefly, it is an RL (reinforcement learning) based system to train an agent to choose the proper compression quality level $ c $ for one image to be compressed by JPEG. We discuss the formulation, agent design, reinforcement learning framework, feedback reward, and inference-estimation-querying-retraining mechanism separately in the following subsections. We provide experimental details of all the hyperparameters in Sec. \ref{sec: evaluation}. %% \\

@@

% \colorbox{red}{notation table}

Without loss of generality, we denote the cloud deep learning service as $ \vec{y}_i = M(x_i) $ that provides a predicted result list $ \vec{y}_i $ for each input image $ x_i $, and it has a baseline output $ \vec{y}_{\rm ref} = M(x_{\rm ref}) $ for each reference input $ x \in X_{\rm ref} $. We use this $ \vec{y}_{\rm ref} $ as the ground truth label, and for each image $ x_c $ compressed at compression quality level $ c $, the output $ \vec{y}_c = M(x_c) $. Therefore, we have an accuracy metric $ \mathcal{A}_c $ by comparing $ \vec{y}_{\rm ref} $ and $ \vec{y}_c $. In general, we use the top-5 accuracy as the following $ \mathcal{A} $, the same as the classification metric of ILSVRC2012~\cite{ILSVRC12}.

@@

Where $ j = 1,...,5 $ indicates the prediction labels at top-5 score, $ k = 1,...,{\rm length}(\vec{y}_{\rm ref}) $ means that if anyone of the top-5 predicted labels matches one of the predictions from $ \vec{y}_{\rm ref} $, it would be regarded as a correct prediction. In general, we cannot get the cloud deep learning model's in-layer details (e.g., softmax probabilities) for a cloud deep learning service, therefore we use a binary hard label $ d(x, y) \in \{0, 1\} $ to evaluate the accuracy. %% $ d(x, y) \in \{0, 1\} $

We also denote JPEG input images as $ f_{ic} = J(x_i, c) $ that for an input image $ x_i $ and a given compression quality level $ c $, and it outputs a compressed file $ f_{ic} $ at the size of $ s_{ic} $. Especially for a reference compression quality level $ c_{\rm ref} $, the compressed file size is $ s_{\rm ref} $. Besides, the input image from a specific location usually belongs to a particular contextual group. For example, in daytime scenery, the input images are expected to have a bright background and high contrast while nighttime images are usually gray-scaled thermal images. Therefore, the agent in one place and one scenery does not need to know all the contextual features in all places and all sceneries. We formulate this as contextual group $ \mathcal{X} $. This contextual grouping concept is also discussed in the study ~\cite{mcdnn}.

Initially, the agent tries different compression quality levels $ c_{\min} < c < c_{\max}, c \in \mathbb{N} $ to obtain compressed image $ x_c $ from input image $ x $, and an image compressed at a reference level $ c_{\rm ref} $ is also uploaded to the cloud to obtain $ \vec{y}_{\rm ref} $. Comparing the two uploaded instances $ \{x_{\rm ref}, x_c\} $ and cloud recognition results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $, we can obtain the reference file size $ s_{\rm ref} $ and compressed file size $ s_c $, therefore compute the file compression ratio $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $.

@@

The RL agent is expected to give a proper compression quality level $ c $ that minimizing the file size $ s_c $ while keeping the accuracy $ \mathcal{A} $. For the RL agent, the input features are continuous numerical vectors, and the expected output is discrete compression quality level $ c $, therefore we can use Deep Q-learning Network \cite{DQN} as the RL agent. But naive Deep Q-learning Network can't work well in this task because of the following challenges: %% \\

\begin{itemize}
    \item The state space of reinforcement learning is too large, and to preserve enough details, we have to add many layers and nodes to the neural network, making the RL agent extremely difficult to converge. 
    \item It takes a long time to train one step in a large inference neural network, making the training process too time-consuming.
    \item The RL agent starts training from random trials and starts learning after it finds better feedback reward. When training from a randomly initialized neural network, the feedback reward is very sparse, making it difficult for the agent to learn.
\end{itemize}

@@

\subsection{Reinforcement Learning Framework}

@@

Based on this insight, we formulate the feature extractor's output $ \mathcal{E}(J(\mathcal{X}, c)) $ as \emph{states} and the compression quality level $ c $ as discrete \emph{actions}. In our system, to accelerate training, we define 10 discrete actions to indicate 10 compression quality levels of JPEG ranging from $ 5, 15, ...,95 $. We denote the \emph{action-value function} as $ Q(\phi(\mathcal{E}(f_t)), c; \theta) $, then the optimal compression quality level at time $ t $ is $ c_t = {\rm argmax}_cQ(\phi(\mathcal{E}(f_t)), c; \theta) $ where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $. In such reinforcement learning formulation, the training phase is to minimize a loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where $ s = \mathcal{E}(f_t) $, and $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $ is the target for the iteration $ i $. Especially, $ r $ is the feedback reward, and $ \rho(s, c) $ is a probability distribution over sequences $ s $ and compression quality level $ c $~\cite{DQN}. When minimizing the distance of the action-value function's output $ Q(\cdot) $ and target $ y_i $, the action-value function $ Q(\cdot) $ outputs a more accurate estimation of an action.

In such a formulation, it is similar to the Deep Q-learning Network problem but not the same. Different from conventional reinforcement learning, the interactions between the agent and environment are infinite, therefore there is no signal from the environment telling that an episode has finished. Therefore, we train the RL agent intermittently at a manual interval of $ T $ after the condition $ t \geq T_{\rm start} $ guaranteeing that there are enough transitions in the memory buffer $ \mathcal{D} $. In the training phase, the RL agent firstly takes some random trials to observe the environment's reaction, and we decrease the randomness when training. All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its action by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $. The training procedure would converge as the agent's randomness keeps decaying. Finally, the agent's action is based on its historical optimal experiences. The training procedure is presented in Algorithm \ref{alg: rl-train}, and we list the parameters in Sec.~\ref{sec: evaluation}.

\begin{algorithm}[htbp]
    \caption{Training RL agent $ \phi $ in environment $ \{\mathcal{X}, M\} $}
    \label{alg: rl-train}
    \begin{algorithmic}[1]
        \STATE Initialize replay memory buffer $ \mathcal{D} $ to capacity $ N $
        \STATE Initialize action-value function $ Q $ with random weights $ \theta $
        \STATE Initialize sequence $ s_1 = \mathcal{E}\big(J(x_1, c_1)\big), x_1 \in \mathcal{X} $ and $ \phi_1 = \phi(f_1) $
        \FOR {t = 1, $ K $}
        \STATE With probability $ \epsilon $ select a random compression level $ c_t $ otherwise select $ c_t = {\rm argmax}_cQ\Big(\phi\big(\mathcal{E}(f_t)\big), c; \theta\Big) $
        \STATE Compress image $ x_t $ at quality $ c_t $ and upload it to the cloud to get result $ (\vec{y}_{\rm ref}, \vec{y}_c) $ and calculate reward $ r = R(\Delta s, \mathcal{A}_c) $
        \STATE Set $ s_{t+1} = s_t $, generate $ c_t, x_{t+1} $ and preprocess $ \phi_{t+1} = \phi \big(\mathcal{E}(f_{t+1})\big) $
        \STATE Store transition $ (\phi_t, c_t, r_t, \phi_{t+1}) $ in $ \mathcal{D} $
        \IF {$ t \mod T == 0 $ and $ t \geq T_{\rm start} $}
        \STATE Sample randomly mini-batch of transitions \\ $ (\phi_j, c_j, r_j, \phi_{j+1}) $ from memory buffer $ \mathcal{D} $
        \STATE Set $ y_i = r_j + \gamma \max_{c'}Q(\phi_{j+1}, c'; \theta) $
        \STATE Compute decay exploration rate \\
        $ \epsilon = 
        \begin{cases}
        \mu_{\rm dec}\cdot \epsilon & \text{ if } \ \mu_{\rm dec}\cdot \epsilon > \epsilon_{\min} \\ 
        \epsilon_{\min}             & \text{ if } \ \mu_{\rm dec}\cdot \epsilon \leq \epsilon_{\min}
        \end{cases} $
        \STATE Perform a gradient descent step on \\ $ \big(y_j - Q(\phi_j, c_j; \theta)\big)^2 $ according to ~\cite{DQN}
        \ENDIF
        \ENDFOR
    \end{algorithmic}
\end{algorithm}

\subsection{Feedback Reward Design}

In our solution, the agent is trained by the feedback reward from the environment $ \{\mathcal{X}, M\} $. In the above formulation, we defined compression rate $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $ in compression quality level $ c $. Basically, we want the agent to choose a proper compression quality level that minimizing the file size while remaining acceptable accuracy, therefore the overall reward $ r $ should be in proportion to the accuracy $ \mathcal{A} $ while in inverse proportion to the compression ratio $ \Delta s $. We introduce two linear factors $ \alpha $ and $ \beta $ to form a linear combination $ r = \alpha \mathcal{A} - \Delta s + \beta $ as the reward function $ R(\Delta s, \mathcal{A}) $. %% \\

@@

As a running system, we introduce an inference-estimation-querying-retraining mechanism to cope with the scenery change in the inference phase, building a system with different components to inferring, capturing the scenery change, then either reloading or retraining the RL agent based on the performance of the cached model. The overall system diagram is illustrated in Figure \ref{fig: diagram}.

@@

%% The system diagram is shown in Figure \ref{fig: diagram}.
We build up the memory buffer $ \mathcal{D} $ and RL (reinforcement learning) training kernel based on the compression and upload driver. When the RL kernel is called, it will load transitions from the memory buffer $ \mathcal{D} $ to train the compression quality level predictor $ \phi $. When the system is deployed, the pre-trained RL agent $ \phi $ guides the compression driver to compress the input image with an adaptive compression quality level $ c $ according to the input image, then uploads the compressed image to cloud. %% \\

After the AdaCompress is deployed, the input images scenery context $ \mathcal{X} $ may change (e.g., day to night, sunny to rainy), when the scenery changes, the older RL agent's compression selection strategy may not be suitable anymore, causing the overall accuracy decreases. To cope with the scenery change, we invoke an estimator with a probability $ p_{\rm est} $. We do this by generating a random value $ \xi \in (0,1) $ and comparing it to $ p_{\rm est} $. If $ \xi \leq p_{\rm est} $ the estimator would be invoked, and AdaCompress would upload the reference image $ x_{\rm ref} $ along with the compressed image $ x_i $ to obtain $ \vec{y}_{\rm ref} $ and $ \vec{y}_i $, therefore calculate $ \mathcal{A}_i $, and save the transition $ (\phi_i, c_i, r_i, \mathcal{A}_i) $ to the memory buffer $ \mathcal{D} $. The estimator also compares the recent $ n $ steps' average accuracy $ \bar{\mathcal{A}}_n $ and the initial accuracy threshold $ \mathcal{A}_0 $ in memory $ \mathcal{D} $. Once the recent average accuracy is much lower than the initial accuracy threshold, the estimator would query an RL agent model to replace the current agent model and test the performance of the reloaded model. To test the reloaded model's performance, the estimator computes the average accuracy $ \bar{\mathcal{A}}^*_n $. If $ \bar{\mathcal{A}}^*_n $ is still lower than the accuracy threshold, the estimator would invoke the RL training kernel to retrain the agent. Once the estimator discovers that the trained reward is higher than the reward threshold, it would stop the training kernel, cache the trained RL agent and switch back to the normal inference state.

Since the reference image $ x_{\rm ref} $ and the compressed image $ x_i $ are both needed in the retraining phase, causing a large uploading file size overhead, especially when the scenery changes frequently (e.g., day to night, then night to day). To avoid unnecessary upload traffic load in the retraining phase, we build up the model caching library to cache the trained RL agent models. When capturing the scenery change, we query a pre-trained model from the model caching library rather than retraining from scratch. %% \\

AdaCompress adaptively switch itself between four states. The switching policy is shown as Figure~\ref{fig: state-switching}.

%\begin{figure}[H]
%    \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.8cm, semithick]
%    \tikzstyle{every state}=[ellipse, align=center, draw=blue, text=black]
%    
%    \node[initial, state] (B)                    {inference};
%    \node[state]         (C) [below right of=B] {retrain};
%    \node[state]         (D) [above right of=C] {estimate};
%    
%    \path   (B) edge [loop above] node {$ \xi > p_{\rm est} $} (B)
%    (B.10)    edge                node {$ \xi \leq p_{\rm est} $} (D.170)
%    (C) edge [below left]      node {$ \bar{r}_n > r_{\rm th} $} (B)
%    edge [loop below] node {$ \bar{r}_n \leq r_{\rm th} $}     (C)
%    (D) edge [loop right] node {$ \xi \leq p_{\rm est} $} (D)
%    (D.190)    edge              node {$ \xi > p_{\rm est} $} (B.-10)
%    (D.225)    edge [below right]      node {$ \bar{\mathcal{A}_n} < \mathcal{A}_0 $} (C);
%    \end{tikzpicture}
%    % \vspace{-0.3cm}
%    \caption{State switching policy}
%    \label{fig: state-switching}
%    %\vspace{-0.8cm}
%\end{figure}

\begin{figure}[H]
    \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2.1cm, semithick]
    \tikzstyle{every state}=[ellipse, align=center, draw=blue, text=black]

    \node[initial, state] (B)                    {inference};
    \node[state]         (C) [below of=B] {retraining};
    \node[state]         (D) [right of=B, node distance=4cm] {estimation};
    \node[state]         (E) [right of=C, node distance=4cm] {model querying};
%    \node[state][rectangle]   (F) [below right of=C, node distance=2.5cm] {Model Library};

@@

\subsubsection{\textbf{Inference:}}

For most times, AdaCompress runs in this state. In this state, only the compressed images are uploaded to the cloud to achieve minimum uploading file size overhead. To keep a stable accuracy performance even the input image scenery changes, the agent would occasionally switch to the estimation state with the probability of $ p_{\rm est} $, meanwhile remain the inference state with the probability of $ 1 - p_{\rm est} $. %% \\

\subsubsection{\textbf{Estimation:}}

In this state, the reference image $ x_{\rm ref} $ and compressed image $ x_i $ are uploaded to the cloud simultaneously to obtain $ \vec{y}_{\rm ref} $ and $ \vec{y}_i $ which are used to calculate $ \mathcal{A}_i $. In each epoch $ i $ the transition $ (\phi_i, c_i, r_i, \mathcal{A}_i) $ is logged in a memory buffer $ \mathcal{D} $. When the average accuracy $ \bar{\mathcal{A}}_n $ of the latest $ n $ steps is higher than the accuracy threshold $ \mathcal{A}_0 $, it stays in the estimation state with the probability of $ p_{\rm est} $ or switches back into the inference state with the probability of $ 1 - p_{\rm est} $. Once the average accuracy $ \bar{\mathcal{A}}_n $ is lower than the initial accuracy threshold $ \mathcal{A}_0 $, indicating that the current agent is no more suitable for the current input image scenery, AdaCompress turns into the model querying state and loads a new RL agent model from the model caching library. %% \\

Therefore, the estimating probability of $ p_{\rm est} $ is vital to the whole system. On the one hand, the estimator should be invoked occasionally to estimate current agent's accuracy, so that to capture the scenery change on time; on the other hand, the estimator uploads the reference image $ x_{\rm ref} $ along with the compressed image, therefore the uploading file size overhead is greater than the conventional benchmark solution, causing higher upload traffic load. %% \\

@@

With this definition, an intuitive formulation of the change of $ p_{\rm est} $ is in inverse proportion of the gradient of $ \mathcal{A} $, meaning that when the recent accuracy is going down, the estimation probability $ p_{\rm est} $ would increase. We formulate that $ p'_{\rm est} = p_{\rm est} + \omega \nabla \bar{\mathcal{A}} $ where $ \omega $ is a scaling factor. With this recursive formula, we have the general term of $ p_{\rm est} $ with an initial estimation probability $ p_0 $ is $p_{\rm est} = p_0 + \omega \sum_{i=0}^{N} \nabla \bar{\mathcal{A}_i} $.

\subsubsection{\textbf{Model Querying:}}

The model querying state is designed to cope with the scenery change before retraining. It loads a new RL agent model from the model caching library and tests whether the loaded agent model is suitable for the current scenery by re-calculating the average accuracy. If the new average accuracy $ \bar{\mathcal{A}}^*_n $ is higher than the accuracy threshold $ \mathcal{A}_0 $, indicating that the loaded agent model is suitable for the current scenery, AdaCompress would switch back to the normal inference state using the loaded agent model. Otherwise, AdaCompress would switch into the retraining state and invokes the RL training kernel to retrain a new RL agent for the current scenery.

In this way, AdaCompress is capable to cope with the scenery change in a cached ``memory'' manner, avoiding retraining the agent model at every scenery change, therefore cutting down the uploading file size overhead. Meanwhile, the agent caching strategy would cause a little storage overhead on local terminal devices.

\subsubsection{\textbf{Retraining:}}

>>>>

A brief framework of AdaCompress is shown in Figure~\ref{fig: framework}. Briefly, it is an reinforcement learning (Rl)-based system to train an agent to choose the proper compression quality level $ c $ for one image to be compressed by JPEG. We discuss the formulation, agent design, reinforcement learning-based framework, reward feedback, and \emph{inference-estimation-querying-retraining} mechanism separately in the following subsections. We provide experimental details of all the hyperparameters in Sec.~\ref{sec: evaluation}. %% \\

@@

% \colorbox{red}{notation table}
Without loss of generality, we denote the cloud-based deep learning service as $ \vec{y}_i = M(x_i) $ that provides a predicted result list $ \vec{y}_i $ for each input image $ x_i $, and it has a baseline output $ \vec{y}_{\rm ref} = M(x_{\rm ref}) $ for each reference input image $ x \in X_{\rm ref} $. We use this $ \vec{y}_{\rm ref} $ as the ground truth label, and for each image $ x_c $ compressed at compression quality level $ c $, the output $ \vec{y}_c = M(x_c) $. Therefore, we have an accuracy metric $ \mathcal{A}_c $ by comparing $ \vec{y}_{\rm ref} $ and $ \vec{y}_c $. In general, we use the top-5 accuracy as the following $ \mathcal{A} $, the same as the classification metric of ILSVRC2012~\cite{ILSVRC12}.

@@

Where $ j = 1,...,5 $ indicates the prediction labels at top-5 score, meaning that if anyone of the top-5 predicted labels matches the ground truth label $ \vec{y}_{\rm ref} $, it would be regarded as a correct prediction. In general, we cannot get the cloud-based deep learning model's in-layer details (e.g., softmax probabilities) for a cloud-based deep learning service, therefore we use a binary hard label $ d(x, y) \in \{0, 1\} $ to evaluate the accuracy. %% $ d(x, y) \in \{0, 1\} $

We also denote JPEG input images as $ f_{ic} = J(x_i, c) $ that for an input image $ x_i $ and a given compression quality level $ c $, and it outputs a compressed file $ f_{ic} $ at the size of $ s_{ic} $. Especially for a reference compression quality level $ c_{\rm ref} $, the compressed file size is $ s_{\rm ref} $. Besides, the input image from a specific location usually belongs to a particular contextual group. For example, in daytime scenery, the input images are expected to have a bright background and high contrast while nighttime images are usually gray-scaled thermal images. Therefore, the agent in one place and one scenery does not need to know all the contextual features in all places and all ``sceneries''. We formulate this as contextual group $ \mathcal{X} $. This contextual grouping concept is also discussed in the study~\cite{mcdnn}.

Initially, the agent tries different compression quality levels $ c_{\min} < c < c_{\max}, c \in \mathbb{N} $ to obtain compressed image $ x_c $ from input image $ x $, and an image compressed at a reference level $ c_{\rm ref} $ is also uploaded to the cloud-end to obtain $ \vec{y}_{\rm ref} $. Comparing the two uploaded instances $ \{x_{\rm ref}, x_c\} $ and cloud-end recognition results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $, we can obtain the reference file size $ s_{\rm ref} $ and compressed file size $ s_c $, therefore compute the file compression ratio $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $.

@@

The RL agent is expected to give a proper compression quality level $ c $ that minimizing the file size $ s_c $ while keeping the accuracy $ \mathcal{A} $. For the RL agent, the input features are continuous numerical vectors, and the expected output is discrete compression quality level $ c $, therefore we can use the Deep Q-learning Network~ as the RL agent. But naive the Deep Q-learning Network can't work well in this task because of the following challenges: %% \\

\begin{itemize}
    \item The state space of reinforcement learning is too large, and to preserve enough details, we have to add many layers and nodes to the neural network, making the RL agent extremely difficult to converge. 
    \item It takes a long time to train one step in a large inference neural network, making the training process too time-consuming.
    \item The RL agent starts training from random trials and learns from the reward feedback. When training from a randomly initialized neural network, the reward feedback is very sparse, making it difficult for the agent to learn.
\end{itemize}

@@

\subsection{reinforcement learning-based Framework}

@@

Based on this insight, we formulate the feature extractor's output $ \mathcal{E}(J(\mathcal{X}, c)) $ as \emph{states} and the compression quality level $ c $ as discrete \emph{actions}. In our system, to accelerate training, we define 10 discrete actions to indicate 10 compression quality levels of JPEG ranging from $ 5, 15, ...,95 $. We denote the \emph{action-value function} as $ Q(\phi(\mathcal{E}(f_t)), c; \theta) $, and the optimal compression quality level at time $ t $ is $ c_t = {\rm argmax}_cQ(\phi(\mathcal{E}(f_t)), c; \theta) $ where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $. In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where $ s = \mathcal{E}(f_t) $, and $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $ is the target for each iteration. Especially, $ r $ is the reward feedback, and $ \rho(s, c) $ is a probability distribution over sequences $ s $ and compression quality level $ c $~\cite{DQN}. When minimizing the distance of \emph{action-value function}'s output $ Q(\cdot) $ and target $ y_i $, the \emph{action-value function} $ Q(\cdot) $ outputs a more accurate estimation of an action.

In such a formulation, it is similar to the Deep Q-learning Network problem but not the same. Different from conventional reinforcement learning, the interactions between the agent and environment are infinite, i.e., there is no signal from the environment telling that an episode has finished. Therefore, we train the RL agent intermittently at a manual interval of $ T $ after the condition $ t \geq T_{\rm start} $ guaranteeing that there are enough transitions in the memory buffer $ \mathcal{D} $. In the training phase, the RL agent firstly takes some random trials to observe the environment's reaction, and decreases the randomness when training. All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its \emph{action} by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $. The training procedure would converge when the agent's randomness keeps decaying. Finally, the agent's action is based on its historical ``optimal'' experiences. The training procedure is presented in Algorithm~\ref{alg: rl-train}, and we list the parameters in Sec.~\ref{sec: evaluation}.

\begin{algorithm}[htbp]
    \caption{Training RL agent $ \phi $ in environment $ \{\mathcal{X}, M\} $}
    \label{alg: rl-train}
    \begin{algorithmic}[1]
        \STATE Initialize replay memory buffer $ \mathcal{D} $ to capacity $ N $
        \STATE Initialize action-value function $ Q $ with random weights $ \theta $
        \STATE Initialize sequence $ s_1 = \mathcal{E}\big(J(x_1, c_1)\big), x_1 \in \mathcal{X} $ and $ \phi_1 = \phi(f_1) $
        \FOR {t = 1, $ K $}
        \STATE With probability $ \epsilon $ select a random compression level $ c_t $ otherwise select $ c_t = {\rm argmax}_cQ\Big(\phi\big(\mathcal{E}(f_t)\big), c; \theta\Big) $
        \STATE Compress image $ x_t $ at quality $ c_t $ and upload it to the cloud to get result $ (\vec{y}_{\rm ref}, \vec{y}_c) $ and calculate reward $ r = R(\Delta s, \mathcal{A}_c) $
        \STATE Set $ s_{t+1} = s_t $, generate $ c_t, x_{t+1} $ and preprocess $ \phi_{t+1} = \phi \big(\mathcal{E}(f_{t+1})\big) $
        \STATE Store transition $ (\phi_t, c_t, r_t, \phi_{t+1}) $ in $ \mathcal{D} $
        \IF {$ t \mod T == 0 $ and $ t \geq T_{\rm start} $}
        \STATE Sample randomly mini-batch of transitions \\ $ (\phi_j, c_j, r_j, \phi_{j+1}) $ from memory buffer $ \mathcal{D} $
        \STATE Set $ y_i = r_j + \gamma \max_{c'}Q(\phi_{j+1}, c'; \theta) $
        \STATE Compute decay exploration rate \\
        $ \epsilon = 
        \begin{cases}
        \mu_{\rm dec}\cdot \epsilon & \text{ if } \ \mu_{\rm dec}\cdot \epsilon > \epsilon_{\min} \\ 
        \epsilon_{\min}             & \text{ if } \ \mu_{\rm dec}\cdot \epsilon \leq \epsilon_{\min}
        \end{cases} $
        \STATE Perform a gradient descent step on \\ $ \big(y_j - Q(\phi_j, c_j; \theta)\big)^2 $ according to~\cite{DQN}
        \ENDIF
        \ENDFOR
    \end{algorithmic}
\end{algorithm}

\subsection{Reward Feedback Design}

In our solution, the agent is trained by the reward feedback from the environment $ \{\mathcal{X}, M\} $. In the above formulation, we defined compression rate $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $ at compression quality level $ c $. Basically, we want the agent to choose a proper compression quality level that minimizing the upload image size while remaining acceptable accuracy, therefore the overall reward $ r $ should be in proportion to the accuracy $ \mathcal{A} $ while in inverse proportion to the compression ratio $ \Delta s $. We introduce two linear factors $ \alpha $ and $ \beta $ to form a linear combination $ r = \alpha \mathcal{A} - \Delta s + \beta $ as the \emph{reward function} $ R(\Delta s, \mathcal{A}) $. %% \\

@@

As a running system, we introduce an \emph{inference-estimation-querying-retraining} mechanism to cope with the scenery change in the inference phase, building a system with different components to inferring, capturing the scenery change, then either re-loading or re-training the RL agent based on the performance of the cached model. The overall system diagram is illustrated in Figure~\ref{fig: diagram}.

@@

%% The system diagram is shown in Figure~\ref{fig: diagram}.
We build up the memory buffer $ \mathcal{D} $ and reinforcement learning (RL) training kernel based on the compression and upload driver. When the RL training kernel is called, it would load transitions from the memory buffer $ \mathcal{D} $ to train the compression quality level predictor $ \phi $. When the system is deployed, the pre-trained RL agent $ \phi $ guides the compression driver to compress the input image at an adaptive compression quality level $ c $ according to the input image, then uploads the compressed image to cloud. %% \\

After the AdaCompress is deployed, the input image scenery context $ \mathcal{X} $ may change (e.g., day to night, sunny to rainy), when the scenery changes, the older RL agent's compression selection strategy may not be suitable anymore, causing the overall accuracy decreases. To cope with the scenery change, we invoke an estimator with a probability $ p_{\rm est} $. We do this by generating a random value $ \xi \in (0,1) $ and comparing it to $ p_{\rm est} $. If $ \xi \leq p_{\rm est} $, the estimator would be invoked, and AdaCompress would upload the reference image $ x_{\rm ref} $ along with the compressed image $ x_i $ to obtain $ \vec{y}_{\rm ref} $ and $ \vec{y}_i $, therefore calculate $ \mathcal{A}_i $, and save the transition $ (\phi_i, c_i, r_i, \mathcal{A}_i) $ to the memory buffer $ \mathcal{D} $. The estimator also compares the recent $ n $ steps' average accuracy $ \bar{\mathcal{A}}_n $ and the initial accuracy threshold $ \mathcal{A}_0 $. Once the recent average accuracy is lower than the initial accuracy threshold, the estimator would query an RL agent model to replace the current agent model and test the performance of the loaded model. To test the loaded model's performance, the estimator computes the average accuracy $ \bar{\mathcal{A}}^*_n $. If $ \bar{\mathcal{A}}^*_n $ is still lower than the accuracy threshold, the estimator would invoke the RL training kernel to re-train the agent. Once the estimator discovers that the trained reward is higher than the reward threshold, it would stop the training kernel, cache the trained RL agent and switch back to the normal inference state.

Since the reference image $ x_{\rm ref} $ and the compressed image $ x_i $ are both needed in the re-training phase, causing a large upload image size overhead, especially when the scenery changes frequently (e.g., day to night, then night to day). To avoid unnecessary upload traffic load in the re-training phase, we build up the model caching library to cache the trained RL agent models. When capturing the scenery change, we query a pre-trained model from the model caching library rather than re-training from scratch. %% \\

AdaCompress adaptively switch itself between four states. The switching policy is shown as Figure~\ref{fig: state-switching}.
%\begin{figure}[H]
%    \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.8cm, semithick]
%    \tikzstyle{every state}=[ellipse, align=center, draw=blue, text=black]
%    
%    \node[initial, state] (B)                    {inference};
%    \node[state]         (C) [below right of=B] {re-train};
%    \node[state]         (D) [above right of=C] {estimate};
%    
%    \path   (B) edge [loop above] node {$ \xi > p_{\rm est} $} (B)
%    (B.10)    edge                node {$ \xi \leq p_{\rm est} $} (D.170)
%    (C) edge [below left]      node {$ \bar{r}_n > r_{\rm th} $} (B)
%    edge [loop below] node {$ \bar{r}_n \leq r_{\rm th} $}     (C)
%    (D) edge [loop right] node {$ \xi \leq p_{\rm est} $} (D)
%    (D.190)    edge              node {$ \xi > p_{\rm est} $} (B.-10)
%    (D.225)    edge [below right]      node {$ \bar{\mathcal{A}_n} < \mathcal{A}_0 $} (C);
%    \end{tikzpicture}
%    % \vspace{-0.3cm}
%    \caption{State switching policy}
%    \label{fig: state-switching}
%    %\vspace{-0.8cm}
%\end{figure}
\begin{figure}[H]
    \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2.1cm, semithick]
    \tikzstyle{every state}=[ellipse, align=center, draw=blue, text=black]

    \node[initial, state] (B)                    {inference};
    \node[state]         (C) [below of=B] {re-training};
    \node[state]         (D) [right of=B, node distance=4cm] {estimation};
    \node[state]         (E) [right of=C, node distance=4cm] {model querying};
%    \node[state][rectangle]   (F) [below right of=C, node distance=2.5cm] {Model Library};

@@

\subsubsection{\textbf{Inference}}

For most times, AdaCompress runs in this state. In this state, only the compressed images are uploaded to the cloud to achieve minimum upload image size overhead. To keep a stable accuracy performance even the input image scenery changes, the agent would occasionally switch to the estimation state with the probability of $ p_{\rm est} $, meanwhile remain the inference state with the probability of $ 1 - p_{\rm est} $. %% \\

\subsubsection{\textbf{Estimation}}

In this state, the reference image $ x_{\rm ref} $ and compressed image $ x_i $ are uploaded to the cloud simultaneously to obtain $ \vec{y}_{\rm ref} $ and $ \vec{y}_i $ which are used to calculate $ \mathcal{A}_i $. In each epoch $ i $ the transition $ (\phi_i, c_i, r_i, \mathcal{A}_i) $ is logged in a memory buffer $ \mathcal{D} $. When the average accuracy $ \bar{\mathcal{A}}_n $ of the latest $ n $ steps is higher than the accuracy threshold $ \mathcal{A}_0 $, it stays in the estimation state with the probability of $ p_{\rm est} $ or switches back into the inference state with the probability of $ 1 - p_{\rm est} $. Once the average accuracy $ \bar{\mathcal{A}}_n $ is lower than the initial accuracy threshold $ \mathcal{A}_0 $, indicating that the current agent is no more suitable for the current input image scenery, AdaCompress would turn into the model querying state and loads a new RL agent model from the model caching library. %% \\

Therefore, the estimation probability of $ p_{\rm est} $ is vital to the whole system. On the one hand, the estimator should be invoked occasionally to estimate current agent's accuracy, so that to capture the scenery change on time; on the other hand, the estimator uploads the reference image $ x_{\rm ref} $ along with the compressed image, therefore the upload image size overhead is greater than the conventional benchmark solution, causing higher upload traffic load. %% \\

@@

With this definition, an intuitive formulation of the change of $ p_{\rm est} $ is in inverse proportion of the gradient of $ \mathcal{A} $, meaning that when the recent accuracy decreases, the estimation probability $ p_{\rm est} $ would increase. We formulate that $ p'_{\rm est} = p_{\rm est} + \omega \nabla \bar{\mathcal{A}} $ where $ \omega $ is a scaling factor. With this recursive formula, we have the general term of $p_{\rm est} = p_0 + \omega \sum_{i=0}^{N} \nabla \bar{\mathcal{A}_i} $, with an initial estimation probability $ p_0 $.

\subsubsection{\textbf{Model Querying}}

The model querying state is designed to cope with the scenery change before re-training. It loads a new RL agent model from the model caching library and tests whether the loaded agent model is suitable for the current scenery by re-calculating the average accuracy. If the new average accuracy $ \bar{\mathcal{A}}^*_n $ is higher than the accuracy threshold $ \mathcal{A}_0 $, indicating that the loaded agent model is suitable for the current scenery, AdaCompress would switch back to the normal inference state using the loaded agent model. Otherwise, AdaCompress would switch into the re-training state and invokes the RL training kernel to re-train a new RL agent for the current scenery.

In this way, AdaCompress is capable to cope with the scenery change in a cached ``memory'' manner, avoiding re-training the agent model at every scenery change, therefore cutting down the upload image size overhead. However, the agent caching strategy would cause a little storage overhead on local terminal devices.

\subsubsection{\textbf{re-training}}

This state is to adapt the agent to the current input image scenery by re-training it with the memory buffer $ \mathcal{D} $, which is similar to the training procedure. The re-training phase has finished upon the recent $ n $ steps' average reward $ \bar{r}_n $ is higher than the user-defined threshold $ r_{\rm th} $. And when the re-training procedure finishes, the memory buffer $ \mathcal{D} $ would be flushed, preparing to save new transitions for the re-training of a next scenery change. The trained RL agent model would be cached in the model caching library and be used to switch to the inference state.
